Rethinking how students learn to design programs

### 2016-04-23 manuscript-body.tex
fix ligatures; add metadata

A growing trend in computer science education research is the collection and analysis of code snapshot data—records of the state of and changes to students’ code as they develop it \cite{jadud_methods_2006,rodrigo_analyzing_2009,spacco_marmoset_2006}. Though specific implementations differ, the general strategy in such projects is that a student event (typically compiling code or saving a file) triggers a procedure that creates a record containing the entire content of all of a student's relevant files, as well as associated metadata (time of save/compilation, for example, and any compiler errors that may have been generated). Mining data from such snapshotting systems has led to large-scale documentation of common student errors \cite{spacco_marmoset_2006}, the development of compile-time detectors to catch common student errors \cite{spacco_software_2005}, and the proposal of formative assessment models to predict student success \cite{jadud_methods_2006,tabanao_predicting_2011}. Building on existing momentum, some researchers are actively pushing for a continued scale-up of how we collect code snapshot data. One current proposal even calls for creating an international database by collecting snapshot data from thousands of introductory programming students worldwide \cite{kolling_building_2012}.

>>>>

A growing trend in computer science education research is the collection and analysis of code snapshot data--records of the state of and changes to students' code as they develop it \cite{jadud_methods_2006,rodrigo_analyzing_2009,spacco_marmoset_2006}. Though specific implementations differ, the general strategy in such projects is that a student event (typically compiling code or saving a file) triggers a procedure that creates a record containing the entire content of all of a student's relevant files, as well as associated metadata (time of save/compilation, for example, and any compiler errors that may have been generated). Mining data from such snapshotting systems has led to large-scale documentation of common student errors \cite{spacco_marmoset_2006}, the development of compile-time detectors to catch common student errors \cite{spacco_software_2005}, and the proposal of formative assessment models to predict student success \cite{jadud_methods_2006,tabanao_predicting_2011}. Building on existing momentum, some researchers are actively pushing for a continued scale-up of how we collect code snapshot data. One current proposal even calls for creating an international database by collecting snapshot data from thousands of introductory programming students worldwide \cite{kolling_building_2012}.
